---
name: "Difference in popular times for trainstations"
title: "Difference in popular times for trainstations"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    social: menu
    surce_code: embed
    orientation: columns
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggswissmaps)
library(shiny)
library(dplyr)
library(ggplot2)


load("city.Rdata")
load("Lakes.RData")
load("Kantone.RData")
library("lubridate")
#aggregate data 
city[city$hour_of_day==24,'hour_of_day'] <- 0 # quick and dirty way, did not changed the other variables.
city$Name <- gsub("FFS","SBB", city$Name)
city$Name
daily <- city%>%
  group_by(URL,date)%>%
  summarise(Difference = as.numeric(mean(diff, na.rm = T)),
                        long = unique(long),
                        lat = unique(lat),
                        Name = unique(Name),
                        group = unique(group))
daily <- daily[, -1]
daily$ind <- as.integer(daily$Difference/10+1)
daily$date <- as.Date(as.character(daily$date), "%Y%m%d")

set_shiny_plot_height <- function(session, output_width_name){
   function() { 
     session$clientData[[output_width_name]] 
   }
}

```


Daily differences in popularity of train stations {data-icon="fa-list"}
====================================================================

## The effects of COVID-19 on Swiss mobility and consumption behaviors

The following data aims at displaying the effects of COVID-19 in relation to people’s mobility and pattern of consumption. This project is inspired and built on a [previous scraping project](https://github.com/philshem/gmaps_popular_times_scraper) and by the opendata community ‘Monitoring COVID-19 effects’ launched by the [statistical office of the Canton Zurich](https://db.schoolofdata.ch/event/7#top).
The data is extrapolated from Google “Popular time” information.
</n>


<b>In the following day, more data on the consumption patterns of the Swiss population will be uploaded.</b>

Tobias Ackermann and Giorgio Cassina


##


### <b>MAPS</b>

Difference in the frequency of people (current frequency – average frequency) for each single train station.

  
```{r}
fillCol(height = 600, flex = c(NA, 1), 
        inputPanel(
          sliderInput("day", "Choose a day:",
                  min = min(daily$date), 
                  max = max(daily$date),
                  value = min(daily$date),
                  animate = TRUE
                  )
        ),
        plotOutput("dailymap", height = "100%")
)

output$dailymap <- renderPlot({
daily[which(daily$date == input$day),]%>%
    ggplot(aes(x = long,y = lat, group = group))+
    geom_polygon(aes(x = long,y = lat, group = group),data = g1k15, fill = "#272d3f")+
    theme_void()+
    coord_equal()+
    geom_polygon(aes(x = long, y = lat, group = group),#lakes
                 data = g1s15, fill ="#3c4252", 
                 alpha = 1, 
                 color = "#3c4252", 
                 size = .1, 
                 lty = "solid")+
    theme(panel.background = element_rect(fill = "#171519",#background
                                          colour = "#171519",
                                          size = 0.5, linetype = "solid"))+
    geom_path(aes(x = long,#adding borders of the cantons
                  y = lat,
                  group = group),
              data = g1k15,
              color = "#3c4252" ,
              size = 0.2)+
      geom_point(aes(x = long, 
                      y = lat, group = group, colour = Difference*-1),
                      data = daily[which(daily$date == input$day),],
                      size = daily[which(daily$date == input$day),]$Difference/10+1)+ 
      scale_colour_gradient(high= "#6897bb",low ="#ffa600", limits = c(-80,20))+
      labs(colour="Difference")
    
})
```



### <b>DEVELOPMENT OVER TIME FOR SINGLE STATIONS</b>


```{r}
fillCol(height = 600, flex = c(NA, 1), 
        inputPanel(
          selectizeInput("station", "Choose a train station", 
                         choices = unique(as.character(daily$Name)), 
                         selected = " Baden FFS")
        ),
        plotOutput("wordPlot", height = "100%")
)

output$wordPlot <- renderPlot({
  daily[daily$Name %in% input$station,] %>%
    ggplot(aes(x=date, y=Difference*-1)) +
      geom_line(color = '#ffa600', size=1) +
      geom_ribbon(aes(ymax = pmax(0,Difference *-1),ymin = pmin(0,Difference*-1)),
                  fill='#ffa600', 
                  alpha=0.4) +
      labs(y="Percentage", x = "Date") +
      ggtitle(paste0(input$station, " - Difference in frequency from \n", min(daily$date)," until ", max(daily$date)))+
      theme(plot.title = element_text(hjust = 0.5), 
            axis.text.x = element_text(angle=45, hjust = 1, vjust = 1),
            panel.background = element_rect(fill='#272d3f'),
            panel.grid.minor = element_blank()) + #,legend.key = element_rect(fill = "#2F2B33"),
      scale_x_date(breaks = unique(daily$date), 
                   date_labels = "%d-%m-%y") +
      scale_y_continuous(breaks = seq(-60,20, by = 20), 
                         limits = c(-60,20), 
                         labels = paste0(seq(-60,20, by = 20),'%'))
},height = 450)
```










